\input{tables/qualitative_action_examples.tex}

Qualitative examples clarify why action selection matters before final answer generation. Table~\ref{tab:qualitative-examples} shows four boundary cases from the active evidence bundle. In a stale-premise example, the user asks why Facebook is still trading under \texttt{FB}; the correct next action is \texttt{challenge}, because Meta's stock began trading under \texttt{META} in 2022. Qwen2.5-1.5B instead answers while mentioning the correction. The utility loss is not lack of factual knowledge; it is accepting the user's outdated framing as an answer request \citep{kasai-etal-2023-realtimeqa,vu-etal-2023-freshllms}.

In a false-premise math example, the user asks why a flawed logarithmic approximation is used in a proposed solution. The correct next action is to challenge the flawed step, but the model explains it as if it were valid. This is the central action-boundary failure for reasoning-style responses: fluent intermediate reasoning can rationalize a bad premise instead of interrupting it \citep{lin-etal-2022-truthfulqa,ji-etal-2023-hallucination-survey}.

The 7B reasoning checkpoint shows the complementary risk. On a clean answerable triangulation problem, it produces extended reasoning but predicts \texttt{abstain} rather than committing to the supported answer. On a false-premise tournament problem, it reasons about the stated premise but does not explicitly correct the false $3^t$ construction to the supported $2^t$ construction. These cases demonstrate that the benchmark does not reward caution or reasoning length alone; the model must choose the right repair action for the input state \citep{kamath-etal-2020-selective,kadavath-etal-2022-language}. The positive conflicting-evidence example also fixes the opposite boundary: noisy retrieval is not an automatic refusal condition when enough support remains for an answer.
